Analyzing Bicycle Parking Safety in Toronto: The Multifaceted Nature of Theft Risk

### 2023-12-19 outputs/paper/paper.qmd
Update the final paper

---
title: "Assessing Bicycle Parking Safety in Toronto: The Multifaceted Nature of Theft Risk."
title-block-banner: true
author: "Yiliu Cao"
thanks: "Code and data from this analysis are available at: https://github.com/yiliuc/Bicycle_Thefts_2023.git"
date: "today"
date-format: "long"
abstract: "This study utilizes data on bicycle thefts sourced from the Toronto Open Data Portal. Preliminary findings indicate a increase propensity for bicycle thefts during summer months. While black mountain bicycles constitute a significant proportion of stolen bikes, it does not necessarily imply they are more susceptible to theft due to their overall prevalence. Moreover, the cost of a bicycle does not seem to influence its theft risk, thieves will not evaluate the price before they steal it. Future research should explore the role of neighborhoods as a potential factor influencing bicycle thefts."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Analyzing Bicycle Parking Safety in Toronto: The Multifaceted Nature of Theft Risk"
title-block-banner: true
author: "Yiliu Cao"
thanks: "Code and data from this analysis are available at: https://github.com/yiliuc/Bicycle_Thefts_2023.git"
date: "2023-10-4"
date-format: "long"
abstract: "This study utilizes data on bicycle thefts sourced from the Toronto Open Data Portal. Preliminary findings indicate a increase propensity for bicycle thefts during summer months. While black mountain bicycles constitute a significant proportion of stolen bikes, it does not necessarily imply they are more susceptible to theft due to their overall prevalence. Moreover, the cost of a bicycle does not seem to influence its theft risk, thieves will not evaluate the price before they steal it. Future research should explore the role of neighborhoods as a potential factor influencing bicycle thefts."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---
